---
title: "Financial Vulnerabilities Dashboard Monitor"
resource_files:
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(readxl)
library(ggplot2)
library(reshape2)
library(plotly)
library(dplyr)
library(knitr)
library(flexdashboard)
if(!require(devtools)) install.packages("devtools")
if(!require(ggpubr)) devtools::install_github("kassambara/ggpubr")
library(ggpubr)
library(shiny)
```

```{r, include=FALSE}
#getwd()
```


```{r read the data files, include=F}
source("heatmap_functions.R")
#shinyoff datapath <- "../DataFolder"
#datapath <- "../DataFolder"
datapath <- "./EXCEL DATA FILES"
excel_files <- list.files(path = datapath, pattern = "xlsm")
excel_files = data.frame(Datafiles = excel_files   )
colnames(excel_files) = "Data files"
```



```{r run the loop to get the last n Quarter risk colors, include = F}

# input file is very important. Uses this to determine which risk tail to use, start time, etc.
#shinyoff input_raw = read_excel(file.path("..", "user_input_file.xlsx"))
input_raw = read_excel(file.path(".", "user_input_file.xlsx"))

# Remove empty rows in input file. 
input_file = input_raw[!is.na(input_raw$file_name),]

# Run loop over the time series.  
risk_data_raw = NULL # Data frame to store all the last 4 risk colors for all the time series.


for (i in 1:nrow(input_file)){
  
    #i = 1 #For debugging.
    print(paste0('i :', i))
    risk_data_current = try(  last_n_Quarters_risk_color(file_name = input_file$file_name[i], 
                         time_series_name = input_file$time_series_name[i], 
                         y = input_file$y[i], 
                         y_axis_label = input_file$y_axis_label[i],
                         Ratio_var_name = input_file$Ratio_var_name[i],                
                         time_series_type = input_file$time_series_type[i], # "Monthly" or "Quarterly"
                         start_ts_at = input_file$start_ts_at[i], # if Quarterly: "Q1 1994", "Q1 1983", if Monthly: "Jan03"
                         risk = input_file$risk[i],            # "two_tailed",  "right_tailed",  "left_tailed"
                         bucket = input_file$bucket[i],
                         sub_bucket = input_file$sub_bucket[i],
                         end_ts_at = input_file$end_ts_at[i], 
                         n_Quarters = 4,  
                         datapath = datapath, 
                         export_R_calculations = "Yes")  )
    
    risk_data_raw = rbind(risk_data_raw, risk_data_current)
    
}

```



```{r Data Cleaning}

################ Do data cleaning

## Omit empty rows that have NA in the time_series. Do not use other columns to do this (do not use risk_data = na.omit(risk_data)).
risk_data_raw = risk_data_raw[!is.na(risk_data_raw$time_series_name),]
risk_data = risk_data_raw

# Search for sub_buckets with only one time_series in the bucket. Do not show the sub_bucket for those ones. 
#Will use the user_input_file to do this. 

#table(input_file$sub_bucket)

# Dertermining the sub_buckets with only one time_series.
sub_bucket_count_data = input_file %>% group_by(sub_bucket) %>% summarise(count = n())
sub_buckets_with_count_1 = sub_bucket_count_data$sub_bucket[sub_bucket_count_data$count == 1]

## Replace the sub_bucket with NA to " " empty string. 
risk_data$sub_bucket = as.character(risk_data$sub_bucket) #First convert sub_bucket from factor type to charactor type
risk_data$sub_bucket[  risk_data$sub_bucket %in% sub_buckets_with_count_1 ] = "   "

#Data check
risk_wide  = dcast(risk_data, time_series_name ~ Period, value.var = "risk_color")

#write.csv(risk_data, "risk_data.csv", row.names = F) #export the table


```


```{r Export the risk_data, include=FALSE}
# Code to export the clean version of the the risk_data.
todaysDate = format(Sys.time(), "%d%m%Y")
risk_data_path = file.path(".", "StoreRiskData") 
dir.create(risk_data_path)  
risk_data_name_and_path = file.path( risk_data_path, paste0( "risk_data_", todaysDate, ".csv"))
write.csv(risk_data, file = risk_data_name_and_path, row.names = F) # in case want to export the data.
```

# Heatmaps

<!-- ## Row 1 {data-height=600} -->

## Column 1 


### `r paste( gsub( " Risk", "", unique(risk_data$bucket)[1] )  , "Bucket")`

```{r}

windowsFonts(Times=windowsFont("Times New Roman"))
require(ggplot2)
require(ggpubr)

bucket_list = unique(input_file$bucket)
strip_text_y = 9

bucket = bucket_list[1]

    data = risk_data[risk_data$bucket == bucket,]
    
    
    # Create the arrow_data_frame which will be used to create the arrow plots.
    
    ## Identify the last 2 quarters.
    ratio_ts_keep = as.character(tail(unique(data$Period), 2))
    
    second_last_Q = ratio_ts_keep[1]
    last_Q = ratio_ts_keep[2]  
    
    ## Now create the row data
    
    arrow_data_frame = data[data$Period == last_Q, ]
    arrow_data_frame = left_join(arrow_data_frame, select(input_file, all_of(c("time_series_name", "risk"))) , by = "time_series_name" )
    
    last_ratio_ts = as.numeric(data$ratio_ts[data$Period == last_Q ])
    second_last_ratio_ts =  as.numeric(data$ratio_ts[data$Period == second_last_Q ])
    
    arrow_vector = last_ratio_ts - second_last_ratio_ts
    
    arrow_data_frame$ratio_ts_diff = arrow_vector
    #!all(arrow_vector == 0)
    #arrow = ifelse(arrow_vector>0, paste0("\\","u2B9D"), paste0("\\", "u2B9F") ) # different type
    
    # Set direction of arrow based on growing or decreasing financial vunerabilities, and based on tail-type risk. 
    
    # arrow = ifelse(risk == 'two_tailed', ifelse(arrow_vector>0, 24, 25), 
    #                ifelse(risk == 'right_tailed', ifelse(arrow_vector>0, 24, 25), 
    #                       ifelse(risk == 'two_tailed', ifelse(arrow_vector>0, 24, 25), .  )) )
    # 
    #  arrow = function(risk, arrow_vector){
    #    
    #    result= if(risk == 'two_tailed') {
    #               ifelse(arrow_vector>0, 24, 25) 
    #          } else if( risk == 'right_tailed' ) {
    #               ifelse(arrow_vector>0, 24, 25)
    #          } else if( risk == 'left_tailed') {
    #               ifelse(arrow_vector>0, 24, 25)
    #          } else {NULL}
    #    
    #     return(result)
    #  }
     
    arrow = ifelse(arrow_vector>0, 24, 25)
    arrow_data_frame$arrow = arrow
    arrow_col = ifelse(arrow == 24, "grey", "white")
    arrow_data_frame$arrow_col = arrow_col

    p1 = ggplot(data, aes(x = Period, y = time_series_name))+
          geom_point(size = 8, color = data$risk_color, shape = "square") +
          labs(title = paste("Financial Vulnerability", "--", bucket),  y = "", x = "") +
          theme(text=element_text(family="Times"),
                axis.text.y = element_text(hjust = 1, face = "plain", size = 16), 
                axis.text.x = element_text(face="bold", size = 16), 
                axis.ticks.x=element_blank(),
                plot.title = element_text(family="Times", face = "bold", size = 20),
                plot.margin = margin(1, 1, 10, 50),
                
                plot.title.position = "plot") +
          scale_x_discrete(position = "top") +
          facet_grid(sub_bucket~., scales = "free", shrink = F, switch = "y")+  #Removed `space="free"` from the facet_grid argument.Now works.07-Nov-2021
          theme(strip.text.y = element_text(size = strip_text_y, face = "bold")) # labeller = label_wrap_gen()
    
    
    p2 = ggplot(arrow_data_frame, aes(x = Period, y = time_series_name))+
          geom_point( shape = arrow_data_frame$arrow, size = 3, fill = arrow_data_frame$arrow_col) + #
          labs(  y = "", x = "") +   
          theme(axis.title.x=element_blank(),
                axis.text.x=element_text(family = "Times",face="bold", size = 16),
                axis.ticks.x=element_blank(),
                axis.title.y=element_blank(),
                axis.text.y=element_blank(),
                axis.ticks.y=element_blank(),
                aspect.ratio = 10/1) +
          scale_x_discrete(breaks=c("Q4 2019"),labels=c("Trend"), position = "top") +
          facet_grid(sub_bucket~.,  scales = "free", shrink = F) + #Removed `space="free"` from the facet_grid argument.Now works.07-Nov-2021
          theme(strip.background = element_blank(),  strip.text.y = element_blank())
    #p2 = p2 + clean_theme()
    
    figure1 = ggarrange(p1,p2, ncol = 2, nrow = 1, widths = c(10, 1), align = "h") 
    renderPlot({annotate_figure(figure1)})
    

```

### `r paste( gsub( " Risk", "", unique(risk_data$bucket)[2] )  , "Bucket")`

    
```{r}
    
strip_text_y = 13
    
    bucket = bucket_list[2]

    data = risk_data[risk_data$bucket == bucket,]
    
    
    # Create the arrow_data_frame which will be used to create the arrow plots.
    
    ## Identify the last 2 quarters.
    ratio_ts_keep = as.character(tail(unique(data$Period), 2))
    
    second_last_Q = ratio_ts_keep[1]
    last_Q = ratio_ts_keep[2]  
    
    ## Now create the row data
    
    arrow_data_frame = data[data$Period == last_Q, ]
    
    last_ratio_ts = as.numeric(data$ratio_ts[data$Period == last_Q ])
    second_last_ratio_ts =  as.numeric(data$ratio_ts[data$Period == second_last_Q ])
    
    arrow_vector = last_ratio_ts - second_last_ratio_ts
    #!all(arrow_vector == 0)
    #arrow = ifelse(arrow_vector>0, paste0("\\","u2B9D"), paste0("\\", "u2B9F") ) # different type
    
    arrow = ifelse(arrow_vector>0, 24, 25)
    arrow_col = ifelse(arrow == 24, "grey", "white")
    arrow_data_frame$arrow = arrow ; arrow_data_frame$ratio_ts_diff = arrow_vector ; arrow_data_frame$arrow_col = arrow_col

    p3 = ggplot(data, aes(x = Period, y = time_series_name))+
          geom_point(size = 8, color = data$risk_color, shape = "square") +
          labs(title = paste("Financial Vulnerability", "--", bucket),  y = "", x = "") +
          theme(text=element_text(family="Times"),
                axis.text.y = element_text(hjust = 1, face = "plain", size = 16), 
                axis.text.x = element_text(face="bold", size = 16), 
                axis.ticks.x=element_blank(),
                plot.title = element_text(family="Times", face = "bold", size = 20),
                plot.title.position = "plot") +
          scale_x_discrete(position = "top") +
          facet_grid(sub_bucket~., scales = "free", shrink = F, switch = "y")+#Removed `space="free"` from the facet_grid argument.Now works.07-Nov-2021
          theme(strip.text.y = element_text(size = strip_text_y, face = "bold")) # labeller = label_wrap_gen()

    
    p4 = ggplot(arrow_data_frame, aes(x = Period, y = time_series_name))+
          geom_point( shape = arrow_data_frame$arrow, size = 3, fill=arrow_data_frame$arrow_col) + #
          labs(  y = "", x = "") +   
          theme(axis.title.x=element_blank(),
                axis.text.x=element_text(family = "Times",face="bold", size = 16),
                axis.ticks.x=element_blank(),
                axis.title.y=element_blank(),
                axis.text.y=element_blank(),
                axis.ticks.y=element_blank(),
                aspect.ratio = 10/1) +
          scale_x_discrete(breaks=c("Q4 2019"),labels=c("Trend"), position = "top") +
          facet_grid(sub_bucket~., scales = "free", shrink = F) +  #Removed `space="free"` from the facet_grid argument.Now works.07-Nov-2021
          theme(strip.background = element_blank(),  strip.text.y = element_blank())
    #p2 = p2 + clean_theme()

    figure2 = ggarrange(p3,p4, ncol = 2, nrow = 1, widths = c(10, 1), align = "h") 
    renderPlot({annotate_figure(figure2)})
    
```

<!-- ## Row 2 {data-height=800} -->

## Column 2 

### `r paste( gsub( " Risk", "", unique(risk_data$bucket)[4] )  , "Bucket")`

    
```{r}    
    
strip_text_y = 13
    
bucket = bucket_list[4]
data = risk_data[risk_data$bucket == bucket,]
    
    
    # Create the arrow_data_frame which will be used to create the arrow plots.
    
    ## Identify the last 2 quarters.
    ratio_ts_keep = as.character(tail(unique(data$Period), 2))
    
    second_last_Q = ratio_ts_keep[1]
    last_Q = ratio_ts_keep[2]  
    
    ## Now create the row data
    
    arrow_data_frame = data[data$Period == last_Q, ]
    
    last_ratio_ts = as.numeric(data$ratio_ts[data$Period == last_Q ])
    second_last_ratio_ts =  as.numeric(data$ratio_ts[data$Period == second_last_Q ])
    
    arrow_vector = last_ratio_ts - second_last_ratio_ts
    #!all(arrow_vector == 0)
    #arrow = ifelse(arrow_vector>0, paste0("\\","u2B9D"), paste0("\\", "u2B9F") ) # different type
    
    arrow = ifelse(arrow_vector>0, 24, 25)
    arrow_col = ifelse(arrow == 24, "grey", "white")
    arrow_data_frame$arrow = arrow ; arrow_data_frame$ratio_ts_diff = arrow_vector ; arrow_data_frame$arrow_col = arrow_col

    p5 = ggplot(data, aes(x = Period, y = time_series_name))+
          geom_point(size = 8, color = data$risk_color, shape = "square") +
          labs(title = paste("Financial Vulnerability", "--", bucket),  y = "", x = "") +
          theme(text = element_text(family = "Times"),
                axis.text.y = element_text(hjust = 1, face = "plain", size = 16), 
                axis.text.x = element_text(face = "bold", size = 16), 
                axis.ticks.x=element_blank(),
                plot.title = element_text(family = "Times", face = "bold", size = 20),
                plot.margin = margin(10, 1, 10, 120),
                
                plot.title.position = "plot") +
          scale_x_discrete(position = "top") +
          facet_grid(sub_bucket~., scales = "free", shrink = F, switch = "y") +#Removed `space="free"` from the facet_grid argument.Now works.07-Nov-2021
          theme(strip.text.y = element_text(size = strip_text_y, face = "bold"))# labeller = label_wrap_gen()
    
    
    p6 = ggplot(arrow_data_frame, aes(x = Period, y = time_series_name))+
          geom_point( shape = arrow_data_frame$arrow, size = 3, fill=arrow_data_frame$arrow_col) + #
          labs(  y = "", x = "") +   
          theme(axis.title.x=element_blank(),
                axis.text.x=element_text(family = "Times",face = "bold", size = 16),
                axis.ticks.x=element_blank(),
                axis.title.y=element_blank(),
                axis.text.y=element_blank(),
                axis.ticks.y=element_blank(),
                aspect.ratio = 10/1) +
          scale_x_discrete(breaks=c("Q4 2019"),labels=c("Trend"), position = "top") +
          facet_grid(sub_bucket~., scales = "free", shrink = F) +  #Removed `space="free"` from the facet_grid argument.Now works.07-Nov-2021
          theme(strip.background = element_blank(),  strip.text.y = element_blank())
    #p2 = p2 + clean_theme()
    
    figure3 = ggarrange(p5,p6, ncol = 2, nrow = 1, widths = c(10, 1), align = "h") 
    renderPlot({annotate_figure(figure3)})
    
```


### `r paste( gsub( " Risk", "", unique(risk_data$bucket)[3] )  , "Bucket")`

    
```{r}
    
strip_text_y = 10
    bucket = bucket_list[3]

    data = risk_data[risk_data$bucket == bucket,]
    
    
    # Create the arrow_data_frame which will be used to create the arrow plots.
    
    ## Identify the last 2 quarters.
    ratio_ts_keep = as.character(tail(unique(data$Period), 2))
    
    second_last_Q = ratio_ts_keep[1]
    last_Q = ratio_ts_keep[2]  
    
    ## Now create the row data
    
    arrow_data_frame = data[data$Period == last_Q, ]
    
    last_ratio_ts = as.numeric(data$ratio_ts[data$Period == last_Q ])
    second_last_ratio_ts =  as.numeric(data$ratio_ts[data$Period == second_last_Q ])
    
    arrow_vector = last_ratio_ts - second_last_ratio_ts
    #!all(arrow_vector == 0)
    #arrow = ifelse(arrow_vector>0, paste0("\\","u2B9D"), paste0("\\", "u2B9F") ) # different type
    
    arrow = ifelse(arrow_vector>0, 24, 25)
    arrow_col = ifelse(arrow == 24, "grey", "white")
    arrow_data_frame$arrow = arrow ; arrow_data_frame$ratio_ts_diff = arrow_vector ; arrow_data_frame$arrow_col = arrow_col

    p7 = ggplot(data, aes(x = Period, y = time_series_name))+
          geom_point(size = 8, color = data$risk_color, shape = "square") +
          labs(title = paste("Financial Vulnerability", "--", bucket),  y = "", x = "") +
          theme(text=element_text(family="Times"),
                axis.text.y = element_text(hjust = 1, face = "plain", size = 16), 
                axis.text.x = element_text(face="bold", size = 16), 
                axis.ticks.x=element_blank(),
                plot.title = element_text(family="Times", face = "bold", size = 20),
                plot.margin = margin(10, 1, 10, 5),
                
                plot.title.position = "plot") +
          scale_x_discrete(position = "top") +
          facet_grid(sub_bucket~., scales = "free", shrink = F, switch = "y") +#Removed `space="free"` from the facet_grid argument.Now works.07-Nov-2021
          theme(strip.text.y = element_text(size = strip_text_y, face = "bold"))
          # labeller = label_wrap_gen()
    
    
    p8 = ggplot(arrow_data_frame, aes(x = Period, y = time_series_name))+
          geom_point( shape = arrow_data_frame$arrow, size = 3, fill=arrow_data_frame$arrow_col) + #
          labs(  y = "", x = "") +   
          theme(axis.title.x=element_blank(),
                axis.text.x=element_text(family = "Times",face="bold", size = 16),
                axis.ticks.x=element_blank(),
                axis.title.y=element_blank(),
                axis.text.y=element_blank(),
                axis.ticks.y=element_blank(),
                aspect.ratio = 10/1) +
          scale_x_discrete(breaks=c("Q4 2019"),labels=c("Trend"), position = "top") +
          facet_grid(sub_bucket~., scales = "free", shrink = F) + #Removed `space="free"` from the facet_grid argument.Now works.07-Nov-2021
          theme(strip.background = element_blank(),  strip.text.y = element_blank()  )
    #p2 = p2 + clean_theme()
    
    figure4 = ggarrange(p7,p8, ncol = 2, nrow = 1, widths = c(10, 1), align = "h") 
    renderPlot({annotate_figure(figure4)}, res =68) 
    
    
    # figure = ggarrange(p1,p2,p3, p4, ncol = 2, nrow = 2, align = "hv") 
    # print(annotate_figure(figure))

```

<!-- Individual heatmaps with subplots -->


# `r unique(risk_data$bucket)[1]`

## Column 1 {data-width=500}

### `r unique(risk_data$bucket)[1]`

```{r, fig.width=8, fig.height=6}


for ( bucket in unique(risk_data$bucket)[1] ) {
  
  #renderPlot({
    heatmap_cat_data(risk_data, bucket) 
  #})
  
}  


```


### 

```{r}
library(dplyr)

selectInput("select_timeseries_from_risk_bucket1", 
            label = "Choose a Time Series", 
            choices = unique( filter(input_file, bucket == unique(risk_data$bucket)[1]  )$time_series_name  ) 
            )

```


## Column 2 {data-width=800}

### Subplots 


```{r, fig.width=10, fig.height=10}
#, fig.width=10, fig.height=15
#print(input$select_timeseries_from_risk_bucket)


renderPlot({
  
input_file_row = filter( input_file, time_series_name ==  input$select_timeseries_from_risk_bucket1) 

create_subplots(file_name = input_file_row$file_name,
                         time_series_name = input_file_row$time_series_name,
                         y = input_file_row$y,
                         y_axis_label = input_file_row$y_axis_label,
                         Ratio_var_name = input_file_row$Ratio_var_name,
                         time_series_type = input_file_row$time_series_type, # "Monthly" or "Quarterly"
                         start_ts_at = input_file_row$start_ts_at, # if Quarterly: "Q1 1994", "Q1 1983", if Monthly: "Jan03"
                         risk = input_file_row$risk,            # "two_tailed",  "right_tailed",  "left_tailed"
                         bucket = input_file_row$bucket,
                         sub_bucket = input_file_row$sub_bucket,
                         end_ts_at = input_file_row$end_ts_at,
                         n_Quarters = 4,
                         datapath = datapath,
                         export_merged_data = "No")
}, res = 120)

```

# `r unique(risk_data$bucket)[2]` 

## Column 1 {data-width=500}

### `r unique(risk_data$bucket)[2]`

```{r, fig.width=7.5, fig.height=7.5}


for (   bucket in unique(risk_data$bucket)[2]   ) {
    (heatmap_cat_data(risk_data, bucket))
} 


```


### 

```{r}

selectInput("select_timeseries_from_risk_bucket2", 
            label = "Choose a Time Series", 
            choices = unique( filter(input_file, bucket == unique(risk_data$bucket)[2]  )$time_series_name  ) 
            )

```


## Column 2 {data-width=800}

### Subplots 

```{r, fig.width=10, fig.height=10}

#print(input$select_timeseries_from_risk_bucket)


renderPlot({
  
  
input_file_row = filter( input_file, time_series_name ==  input$select_timeseries_from_risk_bucket2) 
  
create_subplots(file_name = input_file_row$file_name,
                         time_series_name = input_file_row$time_series_name,
                         y = input_file_row$y,
                         y_axis_label = input_file_row$y_axis_label,
                         Ratio_var_name = input_file_row$Ratio_var_name,
                         time_series_type = input_file_row$time_series_type, # "Monthly" or "Quarterly"
                         start_ts_at = input_file_row$start_ts_at, # if Quarterly: "Q1 1994", "Q1 1983", if Monthly: "Jan03"
                         risk = input_file_row$risk,            # "two_tailed",  "right_tailed",  "left_tailed"
                         bucket = input_file_row$bucket,
                         sub_bucket = input_file_row$sub_bucket,
                         end_ts_at = input_file_row$end_ts_at,
                         n_Quarters = 4,
                         datapath = datapath,
                         export_merged_data = "No")
}, res = 120 )

```

# `r unique(risk_data$bucket)[3]`

## Column 1 {data-width=500}

### `r unique(risk_data$bucket)[3]`

```{r, fig.width=8, fig.height=8}


for (   bucket in unique(risk_data$bucket)[3]  ) {
    (heatmap_cat_data(risk_data, bucket))
} 


```

###

```{r}
library(dplyr)

selectInput("select_timeseries_from_risk_bucket3", 
            label = "Choose a Time Series", 
            choices = unique( filter(input_file, bucket == unique(risk_data$bucket)[1]  )$time_series_name  ) 
            )

```

## Column 1 {data-width=800}

### Subplots



```{r, fig.width=10, fig.height=10}

#print(input$select_timeseries_from_risk_bucket)


renderPlot({
  
input_file_row = filter( input_file, time_series_name ==  input$select_timeseries_from_risk_bucket3) 

create_subplots(file_name = input_file_row$file_name,
                         time_series_name = input_file_row$time_series_name,
                         y = input_file_row$y,
                         y_axis_label = input_file_row$y_axis_label,
                         Ratio_var_name = input_file_row$Ratio_var_name,
                         time_series_type = input_file_row$time_series_type, # "Monthly" or "Quarterly"
                         start_ts_at = input_file_row$start_ts_at, # if Quarterly: "Q1 1994", "Q1 1983", if Monthly: "Jan03"
                         risk = input_file_row$risk,            # "two_tailed",  "right_tailed",  "left_tailed"
                         bucket = input_file_row$bucket,
                         sub_bucket = input_file_row$sub_bucket,
                         end_ts_at = input_file_row$end_ts_at,
                         n_Quarters = 4,
                         datapath = datapath,
                         export_merged_data = "No")
}, res = 120)

```

# `r unique(risk_data$bucket)[4]` 

## Column 1 {data-width=500}

### `r unique(risk_data$bucket)[4]`

```{r, fig.width=6, fig.height=4}


for ( bucket in unique(risk_data$bucket)[4] ) {
    (heatmap_cat_data(risk_data, bucket))
} 

```


### 


```{r}

selectInput("select_timeseries_from_risk_bucket4", 
            label = "Choose a Time Series", 
            choices = unique( filter(input_file, bucket == unique(risk_data$bucket)[4]  )$time_series_name  ) 
            )

```


## Column 2 {data-width=800}

### Subplots  


```{r, fig.width=10, fig.height=10}

#print(input$select_timeseries_from_risk_bucket)


renderPlot({
  
input_file_row = filter( input_file, time_series_name ==  input$select_timeseries_from_risk_bucket4) 

create_subplots(file_name = input_file_row$file_name,
                         time_series_name = input_file_row$time_series_name,
                         y = input_file_row$y,
                         y_axis_label = input_file_row$y_axis_label,
                         Ratio_var_name = input_file_row$Ratio_var_name,
                         time_series_type = input_file_row$time_series_type, # "Monthly" or "Quarterly"
                         start_ts_at = input_file_row$start_ts_at, # if Quarterly: "Q1 1994", "Q1 1983", if Monthly: "Jan03"
                         risk = input_file_row$risk,            # "two_tailed",  "right_tailed",  "left_tailed"
                         bucket = input_file_row$bucket,
                         sub_bucket = input_file_row$sub_bucket,
                         end_ts_at = input_file_row$end_ts_at,
                         n_Quarters = 4,
                         datapath = datapath,
                         export_merged_data = "No")
}, res = 120)

```

